---
title: "Lab 00 - Hello IDS!"
author: "Sam Mitchell"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Izzat", "Brodie"),
  github_username = c("Pizzat123", "Brodieclark23"), 
  colour = c("Green", "Blue"),
  hobby = c("Cycling", "Gym"),
  favourite_number = c(7, 8)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The plot shows the favourite number of each team member on a bar plot with the github username on the x-axis.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Github Usernames", 
          y = "Favourite Number",
          title = "Team Member Favourite Numbers")
```

labs() creates labels for each axis and a title for the plot.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

This visualisation isn't good for the data as most of the points would have only 1 count, and the chart would be very crowded.
A pie chart could be a better visualisation for the larger data frame.